SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations

### 2015-08-18 paper.tex
added to related work

\title{Iterative Imitation Learning with Reduced Human Supervision}

\author{Michael Laskey$^1$,Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny, anca\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}

@@

\begin{abstract}
In traditional imitation learning, a human expert provides a few demonstrations to the robot, which then offline learns a policy to extrapolate these examples to new situations. One challenge is that during execution of the learned policy, a small but inevitable error will amplify, taking the robot further and further away from the regions of state space for which it has seen examples.

Online imitation learning algorithms such as DAgger address this by iteratively executing a trained policy, and asking the expert for examples along the states visted by that policy. These new examples are then aggregated with the previous training data. Such algorithms perform well in new situations, but rely much more heavily on extensive human supervision.

Our goal is to reduce the amount of human supervision required in imitation learning, without sacrificing performance, thus combining the benefits of both online and offline imitation learning approaches. \emph{Our key insight is that the robot should ask for supervision only when its current trained policy has high risk.}

We introduce a method for online imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states. Our algorithm, SHIV (\adnote{spell it out}), follows the trained policy when evaluated risk is low, and asks for human supervision otherwise. Our experiments with a toy car domain, as well as with non-prehensile grasping in clutter, suggest that our method can better utilize a human supervision budget, achieving higher success rates for the same number of queries to the expert.

@@

Thus, instead of planning for the task, the robot directly learns a \emph{policy}, mapping states (or in some cases observations) to actions. It does this based on examples, which are state-action pairs performed by the expert while demonstrating the task. See section 4.1 of \cite{} \adnote{cite Argall LfD survey} for more details.

Traditional approaches work \emph{offline}, passively receiving examples from the expert first, and then approximating a state-action mapping in a second phase. One challenge that these approaches face is that when the robot is executing its trained policy, its actions affect the resulting next state, meaning the visited states are not independent random variables. The practical consequence is that small but often inevitable differences from the supervisor's policy cause the sequence of visited states to drift far from the region of space where the robot has seen training examples, leading to poor performance.

For example, when training an autonomous car to drive on the highway, the car will deviate form the middle of the road and will not be able to recover, because all the trainign examples are from the middle of the road \cite{pomerleau1989alvinn}. Theoretically, the number of mistakes made by the robot in such cases may not scale just linearly, but \emph{quadratically} with the time horizon of the task \cite{} \adnote{cite ross first paper}.

@@

\emph{Online} imitation learning approaches address this by iteratively gathering more examples form the expert \cite{}\adnote{cite Dagger and precusors or follow ups that fit this, e.g. the previous paper form ross}. DAgger is such an algorithm, and works by training a policy on existing examples, but then ``rolling it out'' (execute it) to see what states are likely to occur under this new policy. The expert then provides examples in the new states, correcting the robot's policy, and these examples are aggregated with the previous ones in a training set for the next iteration.

With such algorithms, the number of mistakes has indeed been proven to scale only linearly with the time horizon, as opposed to quadratically \cite{}. DAgger and related algorithms have seen a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.

@@

\adnote{talk about how we define risk}

\adnote{list contributions: }

\adnote{1. an online active imitation learning algorithm that actively decided whether to query the expert or not; we generalize novelty detection, and talk about relation to active learning}

\adnote{2. a theoretical analysis?}

\adnote{3. an experiment in two parts: an indepth analysis on a simple domain, and a comparison to state of the art in a complex nonprehensile manipulation domain}

\adnote{loop back to beginning, we enable the robot to be actively decide when to ask for examples, reducing expert burden}

\adnote{Old intro:}

Consider the problem of teaching a robot a complex task such cooking a meal or as racing a toy car around a track
against human opponents. When the robot is only provided with visual demonstrations without the knowledge or an
underlying cost function describing the task, traditional model based control approaches are often not applicable. In
these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching a robot how to
accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.\adnote{these are very random things to cite for LfD, FYI - there is a survey by Argall that usually gets cited}

One approach to LfD is to train a policy, or a function estimator (either a classifier or regressor), to predict a
supervisor's behavior given training data consisting of pairs of observations (input) and actions (output) performed
while accomplishing a task. Since the robot's actions typically affect the resulting next state, the resulting sequences
of states encountered during the execution of a policy are not independent random variables, thus making statistical
inference challenging. Ross et al. proved that this can cause the error in the policy estimator to compound over the
time and lead to performance degradation that is proportional to the time horizon of the task squared. The intuition
behind this result is that as the robot makes mistakes with respect to the supervisor's policy it drifts from the
distribution it was trained on and might encounter new states it can't generalize to.  Ross and Bagnell overcome this by
presenting an iterative method that first trains a policy on the data observed using standard supervised learning
techniques then tries (or 'rolls out') the policy out in the environment to see what states are likely to occur under
the robot's trained policy.  The supervisor then tells the robot what controls it should applied after each iteration
and the policy is retrained \cite{ross2010reduction}. The DAgger method has been successfully used since to teach a
robot how to follow verbal instructions, achieve state of the art performance on Atari games and fly a quad copter
through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.

During learning, implementations of DAgger require the supervisor to manually provide control inputs that the robot
should have applied for each states it visits when rolling out the current best policy estimate. If the supervisor is a
human or an algorithm with a high time complexity, this can be tedious and expensive. We are hence interested in
reducing the burdon on the supervisor by partitioning the state space into states where the policy can either be
executed autonomously with little expected risk, or where supervisor control input (or 'labels') are likely to be
required due to high 'risk'. A state can be risky for 2 reasons: 1) we encounter a state which has a low density of
training data in its vicinity, which potentially means our policy will mis-predict the supervisor
\cite{tokdar2010importance} 2) the state is near previously visited states, but the control-input is mis-predicted
nonetheless. If an accurate density estimation corresponding to
the pairs of visited states and control signals is available, the first scenario can be captured by regions of
state-space with a low density estimate. Areas of low density are then considered to be risky since an insufficient data
is available to accurately model the demonstrator's policy. This idea is also captured in the notion that 'a trained
model will be able to generalize within the distribution it is trained on' \cite{tokdar2010importance} in statistical
machine learning. The second case arises for example when the current best policy estimate is locally inconsistent with expert
demonstrations.
%
%Vague!!!
%This property can be seen used in importance sampling when data is collected from one distribution, but tested on
%another and has to be re-weighted %to the test distribution \cite{huang2006correcting}. 
%
While the amount of data needed to accurately estimate the density increases exponentially with the dimension of state
space \cite{nadaraya1964estimating}, we can turn to approximate methods which instead attempt to learn an approximate
representation of the quantile levelsets of the distribution. Thus, we propose using a modified version the One Class
SVM method for support estimation that only tries to estimate the level set of the quantile function of the density
\cite{scholkopf2001estimating} at a user-determined quantile threshold which has been used even with high-dimensional
image data \cite{liu2014unsupervised}. Our modification furthermore removes areas of state space from the super-levelset
estimate where the local policy estimate is inconsistent with the expert demonstrations.

To apply our approach, we make the same assumptions as in the case of DAgger: 1) we require access to an environment
where a robot can try out (roll out) policies to sample trajectories and where we are able to collect observation states
and corresponding control inputs along these trajectories. 2) an interface allowing a supervisor to provide control
inputs that should have been applied for states along parts of the rolled out trajectories. 3) We assume that we are
able to collect a series of observations from the environment and the controls applied. 4) Lastly, for our theoretical
analysis to apply, we assume the current observation only depends on the previous observation and control input (i.e.
the Markovian assumption).

Our core contribution is the extension of DAgger to \acro~which incorporates a notion of risk to learning from
demonstrations and reduces supervisor
burdon by asking for supervisor demonstrations only in `risky' states. 
We achieve this by proposing a modified version of the One Class SVM, that both estimates the quantile level sets 
of the distribution of states with demonstrations and additionally
and carves out areas in the support where we know our policy will mis-predict the supervisor, thus identifying states of high
risk.  Our experimental results on a Super Mario Atari video game,  suggest \acro~is able to reach DAgger's
peak performance of surviving for an average of 2200 simulation steps with only 1200 queries to the supervisor, while DAgger required 2800 queries
averaged over 20 levels.
{\color{blue}[-- FINALIZE --]}

\section{Related Work}
\adnote{Should eliminate this section and bring in the important bits in the intro and in the description of the method. For things that belog in the intro, this is a restatement and takes up space. For things that pertain to our method, this is too early and thus hard to explain yet. As a result, the related work section is kind of useless as a section, although much of the content in it can be very useful in other parts of the paper.}

The field of learning from demonstrations has achieved state of the art performance in a variety of areas within robotics
\cite{argall2009survey}. Abbeel et al.~used an iLQR controller based on helicopter trajectories demonstrated by a human expert
to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of
neural networks on video data and tracking markers to imitate the movement of human arms on a 37 degree of freedom humaniod
robot \cite{billard2001learning}. Schulman et al. used a non-linear warping technique based on thin-plate splines
to transer demonstrations of a human controlling a PR2 robot to tie knots with a rope to new and unseen initial
configurations of the~\cite{schulman2013case}.

A subset of research in the field of learning from demonstrations is working within the assumptions that the dynamics of
the robot and the environment are not known and that no access to a cost function describing a given task is available.
Under these assumptions, a set of trajectories and controls can be collected from a supervisor and the policy learning
problem can be treated as a supervised learning problem that determines a function from state space to
controls~\cite{argall2009survey} by means of regression. Pomerleau et al. used this approach on raw image data and
associated control inputs provided by a person driving a car. The authors then learned a policy that allowed a car to
travel on a highway. However, they observed that if the car deviated from the middle of the road the learned policy was
not able to recover, this behavior was attributed to the fact the car only drove in middle of the road while collecting
demonstrations~\cite{pomerleau1989alvinn}. Ross et al. studied this effect and showed that error can accumulate at a
rate quadratic in the time horizon of the policy in general. Ross et al. then proposed a learning algorithm, SMILE, that
stochastically mixes the supervisor's control with the robot's policy control signal during training, thus allowing the
robot to explore states the supervisor had not visited during training~\cite{ross2010efficient}.

Ross and Bagnell improved upon this method with DAgger (Dataset Aggregation) -- an iterative method that first trains a
policy on the data observed using standard supervised learning techniques and then tries, or 'rolls out' the policy in
the environment to see what states are likely to occur under the policy. The supervisor then tells the robot what
controls it should applied at each stage of this roll-out and the policy is retrained with an aggregate of all data seen
before \cite{ross2010reduction}. This algorithm has found widespread adoption in the robotics community. in
\cite{ross2013learning}, a quad-copter using DAgger learned how to fly through a forest using only Histogram of Gradient
(HOG) features extracted from camera images \cite{ross2013learning}. Guo et al. combined DAgger with Deep Q-learning
methods to achieve state of the art performance on a common Atari game benchmark in Reinforcement Learning
\cite{NIPS2014_5421}. Duvallet et al. furthermore used DAgger to teach robots to follow verbal instructions about where
to move sematically in a building with a training set consisting of of humans following similar verbal instructions
\cite{duvallet2013imitation}. Levine et al. very recently extended the iterative learning paradigm through Guided Policy
Search, which replaces the expert with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.

One limitation of DAgger which we address in the present work is that it requires the demonstrator, or supervisor, to
provide control inputs that the expert would have applied for every state encountered along a roll-out of a trajectory at every interation of the
algorithm. Providing these control inputs can be very tedious or expensive both in the case where the `supervisor' is a
human or an algorithm with a high computational demand.

In prior work, Judah et al. proposed applying active learning techniques to improve the learninng ability of an algorithm given a fixed budget. 
\cite{judah2011active,judah2012active}. A drawback of this approach is that it requires us to estimate a complete
density of states from the samples, which can be difficult especially in high dimensions. Furthermore, the  
at each iteration only one labeled state was given. Thus, the robot could potentially be required to try out many more iterations of learning in order to successfully accomplished the task.

\begin{enumerate}
\item Our work is different than traditional pool base active learning for two reasons 1) the data comes in as a stream (i.e. we decided whether to label or not label the sample vs. using a pool base methods) 2) the estimator being trained is part of the parametrization of the distribution of states being encountered at run time, thus violating the i.i.d assumption common in these methods. 
\item Some techniques that can handle these approaches are 1) uncertainty sampling , or measuring some confidence level in a classifier and deciding whether to label or not. 2) Query by committee, which involves sampling a committee of hypothesises from a version space of consistent classifiers 3) Density weighted model, which fitting a density to the unlabeled pool and then using a technique such as uncertainty sampling or query by committee to chose the label with the highest uncertainity times the density under the model. The reason for density weighted model is because the previous approaches are prone to labeling outliers \cite{settles2008analysis}. 
\item Our approach can be considered a query selective strategy that uses the ideas of density weighted models. The level set estimation of the One Class SVM is a binary decision metric of how close a point is to the global support points that define its neighbors. Then our hole punching technique places a "prior" on points that are likely to be misclassified condition on the fact that points nearby are misclassified. Thus, encapsulating both a notion of uncertainity and distance to relative points. 
\item One point that I've been thinking about is that traditional active learning is about training an estimator on some fix distribution and then trying to predict how the estimator will change given new points sampled from the same distribution. Thus most approaches work on the estimator themselves (query by committee sampling different hypotheses or uncertainty sampling measuring confidence). This assumption is violated in DAgger because you are sampling from a new distribution each iteration different from what is trained on. Thus, a confidence threshold such as (distance to hyperplane for an svm) would be misleading because if the point was drawn from a different distribution it could be very far from the hyperplane, but have a different label than that side of the hyperplane. Thus, we purpose not looking at the estimator but at the data itself. We make an assumption that points close to other points in our feature space will have similar labels, but the outliers are unknown and will need new labels. I suggest we run a uncertainty sampling technique vs. SHIV to verify all this.

\end{enumerate}

%[Let's discuss this part]
{\color{blue}[-- IMPROVE THIS PARAGRAPH --]} In order to determine state space regions where a policy is likely to determine
an incorrect control input, we leverage a
property in statistical machine learning that a trained model will be able to generalize within the distribution it is
trained on \cite{tokdar2010importance}. This property is used in importance sampling when data is collected from one
distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. One
approach is to estimate the probability density of states the policy is trained on. However, the amount of data needed to accurately estimate the density scales exponentially in the number of \cite{nadaraya1964estimating}.

Several alternative approaches have been proposed to determine regions of state-space where an estimator is likely fail
to generalize away from the training-data \cite{markou2003novelty}. Knox and Ng \cite{knox1998algorithms} used a nearest
neighbor-based approach by estimating if a point was close to $k$ neighbors, however this approach was shown to be
susceptible to outliers since nearest neighbors mostly incorporate local information about the data. Manevitz and Yousef
\cite{manevitz2002one} trained a neural network filter to try and reconstruct the data and when the reconstruction error
at a point was high, the point was considered as likely to be outside of the estimators domain within which
generalization was possible. Manevitz and Yousef conjecture  that finding the right architecture can be task specific
and might require a large amount of hyperparameter tuning.

Our approach is in particular based on the One Class SVM proposed by Scholk{\"o}pf et al. which estimates a user
defined quantile level set for a collection of training data by solving a convex quadratic program  to find support
vectors. The method has been theoretically shown to approximate the quantile levelset of a density estimate
asymptotically for correctly chosen bandwidth settings and in the case of a normalized Gaussian kernel function \cite{vert2006consistency}. 
In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for outlier detection of high-dimensional 
image data.

>>>>

%\title{Iterative Imitation Learning with Reduced Human Supervision [v11]}
%\title{SHIV:  Reducing Human Supervision for Robot Active Learning [v11]}

\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations}

\author{Michael Laskey$^1$, Sam Staszak, Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny, anca\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}

@@

\begin{abstract}
The SHIV algorithm proposes an alternative to previous query selection methods for stream-based active learning to the non-stationary distributions encountered in robot control.  To reduce operator burden, the Svm-based reduction in Human InterVention (SHIV) algorithm only requests supervision for sufficiently risky or novel states.

In traditional imitation learning, a human expert provides a few demonstrations to the robot, which then \emph{offline} learns a policy to extrapolate these examples to new situations. One challenge is that during execution of the learned policy, a small but inevitable error will amplify, taking the robot further and further away from the regions of state space for which it has seen examples.

\emph{Online} imitation learning algorithms such as DAgger address this challenge by iteratively executing a trained policy, and asking the expert for additional examples along the states visited by that policy. Such algorithms perform well in new situations, but rely much more heavily on extensive human supervision.

Our goal is to reduce the amount of human supervision required in imitation learning, without sacrificing performance. \emph{Our key insight is that the robot should ask for supervision only when its current trained policy has high risk.}

We introduce a method for online imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states. Our algorithm, SHIV (SVM-Based Reduction in Human Intervention), follows the trained policy when evaluated risk is low, and asks for human supervision otherwise. Our experiments with a toy car domain, as well as with non-prehensile grasping in clutter, suggest that our method can better utilize a human supervision budget, achieving higher success rates for the same number of queries to the expert.

@@

Thus, to achieve the task, the robot directly learns a \emph{policy}, mapping states (or in some cases observations) to actions, which eliminates the need for a reward or a model. It does this based on examples, which are state-action pairs performed by the expert while demonstrating the task (see section 4.1 of \cite{argall2009survey}  for more details).

Traditional approaches work \emph{offline}, passively receiving examples from the expert first, and then approximating a state-action mapping in a second phase. One challenge that these approaches face is that when the robot is executing its trained policy, its actions affect the resulting next state. That makes the visited states not independent random variables. The practical consequence is that small but often inevitable differences from the supervisor's policy cause the sequence of visited states to drift far from the region of space where the robot has seen training examples, leading to poor performance.

For example, when training an autonomous car to drive on the highway, the car will deviate form the middle of the road and will not be able to recover, because all the training examples are from the middle of the road \cite{pomerleau1989alvinn}. Theoretically, the number of mistakes made by the robot in such cases may not scale just linearly, but \emph{quadratically} with the time horizon of the task \cite{ross2010efficient}.

@@

\emph{Online} imitation learning approaches address this by iteratively gathering more examples form the expert \cite{grollman2007dogged,ross2010efficient,ross2010reduction}. DAgger is such an algorithm, and works by training a policy on existing examples, but then ``rolling it out'' (execute it) to see what states are likely to occur under this new policy. The expert then provides examples in the new states, correcting the robot's policy, and these examples are aggregated with the previous ones in a training set for the next iteration.

With such algorithms, the number of mistakes has indeed been proven to scale only linearly with the time horizon, as opposed to quadratically \cite{ross2010efficient}. DAgger and related algorithms have seen a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.

@@

States can have high risk for two complementary reasons: (1) they are far from the training examples --- this type of risk is studied under novelty or outlier detection \cite{hodge2004survey}; or (2) they lie in a region that has proven to be difficult to correctly label in the past, despite there being training data in that region.

Our main contribution is integrating this notion of risk into online imitation learning. We introduce SHIV (), which builds on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to evaluate this risk.

We analyze our algorithm on a car track example, studying the risk evaluation method along with its robustness to the selection of a threshold for how risk adverse the robot should be. We also compare it with state of the art online imitation learning on a more complex task of nonprehensile grasping in clutter. Our results suggest that SHIV learns policies with higher success rates for the same budget of expert examples.

Overall, our work enables robots to actively decide when to ask for examples during online imitation learning, reducing the burden on the user and paving the way towards more effective human-robot interactions.

% \adnote{Old intro:}

% Consider the problem of teaching a robot a complex task such cooking a meal or as racing a toy car around a track
% against human opponents. When the robot is only provided with visual demonstrations without the knowledge or an
% underlying cost function describing the task, traditional model based control approaches are often not applicable. In
% these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching a robot how to
% accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.\adnote{these are very random things to cite for LfD, FYI - there is a survey by Argall that usually gets cited}

% One approach to LfD is to train a policy, or a function estimator (either a classifier or regressor), to predict a
% supervisor's behavior given training data consisting of pairs of observations (input) and actions (output) performed
% while accomplishing a task. Since the robot's actions typically affect the resulting next state, the resulting sequences
% of states encountered during the execution of a policy are not independent random variables, thus making statistical
% inference challenging. Ross et al. proved that this can cause the error in the policy estimator to compound over the
% time and lead to performance degradation that is proportional to the time horizon of the task squared. The intuition
% behind this result is that as the robot makes mistakes with respect to the supervisor's policy it drifts from the
% distribution it was trained on and might encounter new states it can't generalize to.  Ross and Bagnell overcome this by
% presenting an iterative method that first trains a policy on the data observed using standard supervised learning
% techniques then tries (or 'rolls out') the policy out in the environment to see what states are likely to occur under
% the robot's trained policy.  The supervisor then tells the robot what controls it should applied after each iteration
% and the policy is retrained \cite{ross2010reduction}. The DAgger method has been successfully used since to teach a
% robot how to follow verbal instructions, achieve state of the art performance on Atari games and fly a quad copter
% through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.

% During learning, implementations of DAgger require the supervisor to manually provide control inputs that the robot
% should have applied for each states it visits when rolling out the current best policy estimate. If the supervisor is a
% human or an algorithm with a high time complexity, this can be tedious and expensive. We are hence interested in
% reducing the burdon on the supervisor by partitioning the state space into states where the policy can either be
% executed autonomously with little expected risk, or where supervisor control input (or 'labels') are likely to be
% required due to high 'risk'. A state can be risky for 2 reasons: 1) we encounter a state which has a low density of
% training data in its vicinity, which potentially means our policy will mis-predict the supervisor
% \cite{tokdar2010importance} 2) the state is near previously visited states, but the control-input is mis-predicted
% nonetheless. If an accurate density estimation corresponding to
% the pairs of visited states and control signals is available, the first scenario can be captured by regions of
% state-space with a low density estimate. Areas of low density are then considered to be risky since an insufficient data
% is available to accurately model the demonstrator's policy. This idea is also captured in the notion that 'a trained
% model will be able to generalize within the distribution it is trained on' \cite{tokdar2010importance} in statistical
% machine learning. The second case arises for example when the current best policy estimate is locally inconsistent with expert
% demonstrations.
% %
% %Vague!!!
% %This property can be seen used in importance sampling when data is collected from one distribution, but tested on
% %another and has to be re-weighted %to the test distribution \cite{huang2006correcting}. 
% %
% While the amount of data needed to accurately estimate the density increases exponentially with the dimension of state
% space \cite{nadaraya1964estimating}, we can turn to approximate methods which instead attempt to learn an approximate
% representation of the quantile levelsets of the distribution. Thus, we propose using a modified version the One Class
% SVM method for support estimation that only tries to estimate the level set of the quantile function of the density
% \cite{scholkopf2001estimating} at a user-determined quantile threshold which has been used even with high-dimensional
% image data \cite{liu2014unsupervised}. Our modification furthermore removes areas of state space from the super-levelset
% estimate where the local policy estimate is inconsistent with the expert demonstrations.

% To apply our approach, we make the same assumptions as in the case of DAgger: 1) we require access to an environment
% where a robot can try out (roll out) policies to sample trajectories and where we are able to collect observation states
% and corresponding control inputs along these trajectories. 2) an interface allowing a supervisor to provide control
% inputs that should have been applied for states along parts of the rolled out trajectories. 3) We assume that we are
% able to collect a series of observations from the environment and the controls applied. 4) Lastly, for our theoretical
% analysis to apply, we assume the current observation only depends on the previous observation and control input (i.e.
% the Markovian assumption).

% Our core contribution is the extension of DAgger to \acro~which incorporates a notion of risk to learning from
% demonstrations and reduces supervisor
% burdon by asking for supervisor demonstrations only in `risky' states. 
% We achieve this by proposing a modified version of the One Class SVM, that both estimates the quantile level sets 
% of the distribution of states with demonstrations and additionally
% and carves out areas in the support where we know our policy will mis-predict the supervisor, thus identifying states of high
% risk.  Our experimental results on a Super Mario Atari video game,  suggest \acro~is able to reach DAgger's
% peak performance of surviving for an average of 2200 simulation steps with only 1200 queries to the supervisor, while DAgger required 2800 queries
% averaged over 20 levels.
% {\color{blue}[-- FINALIZE --]}

\section{Related Work}

Work related to ours can be grouped in two categories: work related to the active learning aspect, and work related to the risk evaluation aspect.

\noindent\textbf{Active Imitation Learning.}
SHIV instantiates \emph{stream-based} active learning ~\cite{atlas1990training,cohn1994improving}, it receives the stream of states induced by executing the current best policy estimate, and actively decides for each state whether to query the expert or not.

Stream-based active learning has two ingredients: a stream, given here by the policy, and a query selection method. Typical query selection methods are estimator-centric: they evaluate the estimator's confidence (e.g. distance from the classification hyperplane \cite{tong2002support}), implicitly assuming a fixed distribution --- that the new data is sampled from the same distribution as the previous training data. Although such methods have been proposed for online imitation learning (see dogged learning \cite{chernova2009interactive,grollman2007dogged}),
online imitation learning violates the fixed distribution assumption because each new policy induces a new distribution of states . Another way to measure confidence is query by committee, which uses a committee of hypothesis classifiers that are trained on different subset of training data and only labels points for which they disagree. Judah et al. has proposed using this approach towards online imitation learning\cite{judah2011active,judah2012active}, however it has been shown when training and test distributions are different this can perform worse than randomly selecting points \cite{burbidge2007active}.

Instead, we contribute a query selection method that is data-centric, evaluating confidence based on novelty
and on historically mislabeled regions. %Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}. 
Our results suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector.

\noindent\textbf{Risk via Novelty Detection.}
One part of our risk definition is the notion that a trained model will be able to generalize within the distribution it is
trained on \cite{tokdar2010importance}. Novelty detection \cite{hodge2004survey} is concerned with recognizing that a sample is outside of this distribution, making it difficult for a model to correctly predict its label.
One approach to novelty detection is to directly estimate the underlying probability density function from which the data is sampled. However, the amount of data needed to accurately do so scales exponentially in the number of dimensions \cite{nadaraya1964estimating}.

An alternative to evaluating the probability of a data point is to measure distance to its nearest neighbors \cite{knox1998algorithms}. However, this approach was shown to be
susceptible to outliers since nearest neighbors mostly incorporate local information about the data \cite{hodge2004survey}.

Our approach is based on the One Class SVM proposed by Scholk{\"o}pf et al., which estimates a particular quantile level set for the training data by solving a convex quadratic program  to find support
vectors. The method has been theoretically shown to approximate the quantile levelset of a density estimate
asymptotically for correctly chosen bandwidth settings and in the case of a normalized Gaussian kernel function \cite{vert2006consistency}. 
In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for novelty detection in high-dimensional 
image data.

% The field of learning from demonstrations has achieved state of the art performance in a variety of areas within robotics
% \cite{argall2009survey}. Abbeel et al.~used an iLQR controller based on helicopter trajectories demonstrated by a human expert
% to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of
% neural networks on video data and tracking markers to imitate the movement of human arms on a 37 degree of freedom humaniod
% robot \cite{billard2001learning}. Schulman et al. used a non-linear warping technique based on thin-plate splines
% to transer demonstrations of a human controlling a PR2 robot to tie knots with a rope to new and unseen initial
% configurations of the~\cite{schulman2013case}.

% A subset of research in the field of learning from demonstrations is working within the assumptions that the dynamics of
% the robot and the environment are not known and that no access to a cost function describing a given task is available.
% Under these assumptions, a set of trajectories and controls can be collected from a supervisor and the policy learning
% problem can be treated as a supervised learning problem that determines a function from state space to
% controls~\cite{argall2009survey} by means of regression. Pomerleau et al. used this approach on raw image data and
% associated control inputs provided by a person driving a car. The authors then learned a policy that allowed a car to
% travel on a highway. However, they observed that if the car deviated from the middle of the road the learned policy was
% not able to recover, this behavior was attributed to the fact the car only drove in middle of the road while collecting
% demonstrations~\cite{pomerleau1989alvinn}. Ross et al. studied this effect and showed that error can accumulate at a
% rate quadratic in the time horizon of the policy in general. Ross et al. then proposed a learning algorithm, SMILE, that
% stochastically mixes the supervisor's control with the robot's policy control signal during training, thus allowing the
% robot to explore states the supervisor had not visited during training~\cite{ross2010efficient}.

% Ross and Bagnell improved upon this method with DAgger (Dataset Aggregation) -- an iterative method that first trains a
% policy on the data observed using standard supervised learning techniques and then tries, or 'rolls out' the policy in
% the environment to see what states are likely to occur under the policy. The supervisor then tells the robot what
% controls it should applied at each stage of this roll-out and the policy is retrained with an aggregate of all data seen
% before \cite{ross2010reduction}. This algorithm has found widespread adoption in the robotics community. in
% \cite{ross2013learning}, a quad-copter using DAgger learned how to fly through a forest using only Histogram of Gradient
% (HOG) features extracted from camera images \cite{ross2013learning}. Guo et al. combined DAgger with Deep Q-learning
% methods to achieve state of the art performance on a common Atari game benchmark in Reinforcement Learning
% \cite{NIPS2014_5421}. Duvallet et al. furthermore used DAgger to teach robots to follow verbal instructions about where
% to move sematically in a building with a training set consisting of of humans following similar verbal instructions
% \cite{duvallet2013imitation}. Levine et al. very recently extended the iterative learning paradigm through Guided Policy
% Search, which replaces the expert with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.

% One limitation of DAgger which we address in the present work is that it requires the demonstrator, or supervisor, to
% provide control inputs that the expert would have applied for every state encountered along a roll-out of a trajectory at every interation of the
% algorithm. Providing these control inputs can be very tedious or expensive both in the case where the `supervisor' is a
% human or an algorithm with a high computational demand.

% In prior work, Judah et al. proposed applying active learning techniques to improve the learninng ability of an algorithm given a fixed budget. 
% \cite{judah2011active,judah2012active}. A drawback of this approach is that it requires us to estimate a complete
% density of states from the samples, which can be difficult especially in high dimensions. Furthermore, the  
% at each iteration only one labeled state was given. Thus, the robot could potentially be required to try out many more iterations of learning in order to successfully accomplished the task.

% \begin{enumerate}
% \item Our work is different than traditional pool base active learning for two reasons 1) the data comes in as a stream (i.e. we decided whether to label or not label the sample vs. using a pool base methods) 2) the estimator being trained is part of the parametrization of the distribution of states being encountered at run time, thus violating the i.i.d assumption common in these methods. 
% \item Some techniques that can handle these approaches are 1) uncertainty sampling , or measuring some confidence level in a classifier and deciding whether to label or not. 2) Query by committee, which involves sampling a committee of hypothesises from a version space of consistent classifiers 3) Density weighted model, which fitting a density to the unlabeled pool and then using a technique such as uncertainty sampling or query by committee to chose the label with the highest uncertainity times the density under the model. The reason for density weighted model is because the previous approaches are prone to labeling outliers \cite{settles2008analysis}. 
% \item Our approach can be considered a query selective strategy that uses the ideas of density weighted models. The level set estimation of the One Class SVM is a binary decision metric of how close a point is to the global support points that define its neighbors. Then our hole punching technique places a "prior" on points that are likely to be misclassified condition on the fact that points nearby are misclassified. Thus, encapsulating both a notion of uncertainity and distance to relative points. 
% \item One point that I've been thinking about is that traditional active learning is about training an estimator on some fix distribution and then trying to predict how the estimator will change given new points sampled from the same distribution. Thus most approaches work on the estimator themselves (query by committee sampling different hypotheses or uncertainty sampling measuring confidence). This assumption is violated in DAgger because you are sampling from a new distribution each iteration different from what is trained on. Thus, a confidence threshold such as (distance to hyperplane for an svm) would be misleading because if the point was drawn from a different distribution it could be very far from the hyperplane, but have a different label than that side of the hyperplane. Thus, we purpose not looking at the estimator but at the data itself. We make an assumption that points close to other points in our feature space will have similar labels, but the outliers are unknown and will need new labels. I suggest we run a uncertainty sampling technique vs. SHIV to verify all this.

% \end{enumerate}

% %[Let's discuss this part]
% {\color{blue}[-- IMPROVE THIS PARAGRAPH --]} In order to determine state space regions where a policy is likely to determine
% an incorrect control input, we leverage a
% property in statistical machine learning that a trained model will be able to generalize within the distribution it is
% trained on \cite{tokdar2010importance}. This property is used in importance sampling when data is collected from one
% distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. One
% approach is to estimate the probability density of states the policy is trained on. However, the amount of data needed to accurately estimate the density scales exponentially in the number of \cite{nadaraya1964estimating}.

% Several alternative approaches have been proposed to determine regions of state-space where an estimator is likely fail
% to generalize away from the training-data \cite{markou2003novelty}. Knox and Ng \cite{knox1998algorithms} used a nearest
% neighbor-based approach by estimating if a point was close to $k$ neighbors, however this approach was shown to be
% susceptible to outliers since nearest neighbors mostly incorporate local information about the data. Manevitz and Yousef
% \cite{manevitz2002one} trained a neural network filter to try and reconstruct the data and when the reconstruction error
% at a point was high, the point was considered as likely to be outside of the estimators domain within which
% generalization was possible. Manevitz and Yousef conjecture  that finding the right architecture can be task specific
% and might require a large amount of hyperparameter tuning.
